Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
update section III

For most of the experiments reported in this paper, the DCASE2013 datatset is considered \cite{giannoulis2013database, 7100934}. To build this dataset, three different recordists visited a wide variety of locations in Greater London over
a period of months and in each
scene recorded a few minutes of audio for each scene type. No
systematic variations in the recordings covaried with scene
type: all recordings were made in moderate weather condi-
tions, and varying times of day and week, and each recordist
recorded each scene type. The dataset is split into a public dataset that can used for optimizing the ASC system and a private dataset used for computing the resulting accuracy using a 5 fold cross validation scheme. The folds used in this paper are the same as the ones used during the challenge.

>>>>

For most of the experiments reported in this paper, the DCASE2013 datatset is considered \cite{giannoulis2013database, 7100934}. To build this dataset, three different recordists visited a wide variety of locations in Greater London over
a period of months and in each
scene recorded a few minutes of audio for each scene type. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type.
The dataset is split into a public dataset that can used for optimizing the ASC system and a private dataset used for computing the resulting accuracy using a 5 fold cross validation scheme. The folds used in this paper are the same as the ones used during the challenge.
